---
title: "Baer_PS2"
author: "Marliese"
date: "10/31/2022"
output: html_document
---


Lets set things up!

```{r}
rm(list = ls())
library(dplyr)
library(ggplot2)
library(here)
```


Bring in the data using here() and convert the variables Costume and Type to factor

```{r}
DF <-read.csv(here("Data", "Halloween_data_PS2.csv"),stringsAsFactors=TRUE)
```


```{r}
DF$Costume<-as.factor(DF$Costume) #convert to factor data type
DF$Type<-as.factor(DF$Type)
```


Examine the dataset with at least 2 functions

```{r}
glimpse(DF)
head(DF)
str(DF)
tail(DF)
names(DF)
summary(DF)
```

Look at the levels of the columns

```{r}
levels(DF$Costume)
levels(DF$Type)
```

Fix any errors you see in the dataset.

I saw that there were issues with the levels because of the way data was entered. Lets correct those errors.

```{r}

no<-which(DF$Costume=="clown"|DF$Costume=="Creepy clown")

DF$Costume[no]<-"creepy clown"


wrong<-which(DF$Costume=="witch"|DF$Costume=="witch ")

DF$Costume[wrong]<-"Witch"


ew<-which(DF$Costume=="wonder woman"|DF$Costume=="Wonder woman")

DF$Costume[ew]<-"Wonder Woman"


thenerve<-which(DF$Type=="scary"|DF$Type=="scary ")

DF$Type[thenerve]<-"Scary"

```


```{r}
DF$Costume <-factor(DF$Costume)
levels(DF$Costume)

DF$Type <-factor(DF$Type)
levels(DF$Type)
```

Much better!


Calculate the mean age of trick-or-treaters and the mean number of pieces of candy
taken broken down by Costume and Type. Use those data to create figure 1, below.
Match figure 1 as closely as you can.


```{r}
Try<-DF%>%
  group_by(Costume,Type)%>%
  summarise(
    avg_age=mean(age),
  avg_candy_pieces=mean(candy_pieces))
```


Make Figure 1

```{r}
ggplot(Try,aes(x=avg_age,y=avg_candy_pieces,colour=Type))+
  geom_point(size=5)+
  xlab("Mean age of kid (years)")+
  ylab("Mean number pieces taken")+
  theme_bw()
```


Next write code that isolates the data for children in “not scary” costumes who are 10 years old or younger 
Use the resulting data to plot a histogram showing the number of kids in each age class and that comes as close as you can to replicating figure 2, below.


```{r}
NS10<-DF%>%
  filter(Type=="Not scary")%>%
  filter(age<=10)
```

Make Figure 2

```{r}
ggplot(NS10, aes(x = age))+
     geom_histogram(bins=4)+
  xlab("age of child")+
  ylab("number")
```



Next, write code that replicates figure 3 below as closely as you can (Hint: try
`coord_flip()` in your ggplot to get the axes reversed so that you can read the costume
choice names).

Make Figure 3

```{r}
ggplot(DF,aes(x=age,y=Costume))+
  geom_boxplot()+
  geom_point(size=4,colour='lightgrey',alpha=0.5)+
  xlab("Child age (years)")+
  ylab("Costume choice")+
  facet_wrap(~Type)
```


All done!


